Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2016-01-31 ijar-npb-ms.tex
Section 8 (with outlook) and only first name initials in Biblography

In this paper we have contributed an imprecise Bayesian nonparametric approach
to system reliability with multiple types of components.
The approach allows modelling partial or imperfect prior knowledge on component failure distributions
in a flexible way through bounds on the functioning probability for a grid of time points, 
and combines this information with test data in an imprecise Bayesian framework.
Component-wise predictions on the number of functioning components
are then combined to bounds for the system survival probability by means of the survival signature.
New results on first-order stochastic dominance for the Beta-Binomial distribution
enable closed-form solutions for these bounds in most cases and 
avoid exponential growth in the complexity of computing the estimate
as the number of components grows.
The widths of the resulting system reliability bounds
reflect the amount of test data, the precision of prior knowledge,
and crucially provide an easily used method to identify 
whether these two information sources are in conflict in a
way which is of consequence to the whole system reliability
estimate.

These methodological contributions can be immediately used in
applications by reliability practitioners as a result of the 
easy to use software tools which have been provided.

%% LOUIS: do we really want outlook?  I am inclined not to
%% discuss this in a non-review/tutorial paper because we
%% don't want to alert others and get scooped on future
%% ideas!
%Upscaling the survival signature to large real-world systems and networks, consisting of thousands of components, is a major challenge.
%However, even for such systems the fact that one only needs to derive the survival signature once for a system is an advantage,
%and also the monotonicity of the survival signature for coherent systems is very useful if one can only derive it partially.  
%
%The survival signature and its use for uncertainty quantification for system
%reliability can be generalized quite straightforwardly, mainly due to the simplicity of this concept.
%For example, one may generalize the system structure function from a binary function to a probability, %\citep[see]{CCM16},
%to reflect uncertainty about system functioning for known states of its components, with a further
%generalization to imprecise probabilities possible. It is also conceptually easy to generalize the
%survival signature to multi-state systems such that it again summarizes the structure function
%in a manner that is sufficient for a range of uncertainty quantifications for the system reliability. 
%
%
%***Extend the model to deal with right-censored observations which are common in the reliability setting.
%The minimal assumption that a component can either fail immediately after censoring or live forever
%will be simple to implement but will lead to high imprecision,
%whereas assuming exchangeability with other surviving components at moment of censoring
%will be more complex to accomodate but will lead to less imprecision.
%This excangeability assumption lies at the core of the Kaplan-Meier estimator \citep{1958:kaplan-meier},
%and has already been adopted by \citet{2004:coolen-yan} in an imprecise probability context.
%
%***right-censoring will also allow to use data from running system,
%to calculate its remaining useful life (RUL).
%

>>>>

%\subsection{Summary}
In this paper we have contributed an imprecise Bayesian nonparametric approach
to system reliability with multiple types of components.
The approach allows modelling partial or imperfect prior knowledge on component failure distributions
in a flexible way through bounds on the functioning probability for a grid of time points, 
and combines this information with test data in an imprecise Bayesian framework.
Component-wise predictions on the number of functioning components
are then combined to bounds for the system survival probability by means of the survival signature.
New results on first-order stochastic dominance for the Beta-Binomial distribution
enable closed-form solutions for these bounds in most cases and 
avoid exponential growth in the complexity of computing the estimate
as the number of components grows.
The widths of the resulting system reliability bounds
reflect the amount of test data, the precision of prior knowledge,
and crucially provide an easily used method to identify 
whether these two information sources are in conflict in a
way which is of consequence to the whole system reliability
estimate.

These methodological contributions can be immediately used in
applications by reliability practitioners as %a result of the 
%easy to use software tools which have been provided.
we provide easy to use software tools.
%for the computation of the survival signature and system reliability bounds.

%% LOUIS: do we really want outlook?  I am inclined not to
%% discuss this in a non-review/tutorial paper because we
%% don't want to alert others and get scooped on future
%% ideas!
%\subsection{Outlook}
%On further avenues for research,
An important next step is to extend the model to include right-censored observations which are common in the reliability setting.
In particular, this allows to use component failure observations from a running system
to calculate its remaining useful life.
%For treatment of censored observations
We see two potential approaches.
First, to obtain lower and upper system reliability bounds 
one can assume that a component either fails immediately after censoring or
continues to function during the entire time horizon.
This minimal assumption will be simple to implement but will lead to high imprecision.
Alternatively, one can assume exchangeability with other surviving components at the moment of censoring.
This approach will be more complex to accomodate but will lead to less imprecision.
Indeed, this assumption lies at the core of the Kaplan-Meier estimator \citep{1958:kaplan-meier},
and has already been adopted by \citet{2004:coolen-yan} in an imprecise probability context.

Upscaling the survival signature to large real-world systems and networks, consisting of thousands of components, is a major challenge.
However, even for such systems the fact that one only needs to derive the survival signature once for a system is an advantage,
and also the monotonicity of the survival signature for coherent systems is very useful if one can only derive it partially.

The survival signature and its use for uncertainty quantification for system
reliability can be generalized quite straightforwardly, mainly due to the simplicity of this concept.
For example, one may generalize the system structure function from a binary function to a probability, %\citep[see]{CCM16},
to reflect uncertainty about system functioning for known states of its components, with a further
generalization to imprecise probabilities possible.
% It is also conceptually easy to generalize the
%survival signature to multi-state systems such that it again summarizes the structure function
%in a manner that is sufficient for a range of uncertainty quantifications for the system reliability.
